figures and calculations for global fisheries management

### 2019-01-12 documents/figs-and-calcs.Rmd
make figure nice

catchshare_pred_plot <- orig_itq_broad_fit %>% 
  ggplot(aes(pred,CatchShare == 1,fill = CatchShare == 1)) + 
  ggridges::geom_density_ridges(show.legend = FALSE) +
  geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
  labs(y = "Is Catch Share?",
       x = "Probability of Catch Share",
       caption = "Classified as catch share if p>0.5")

@@

pROC::ggroc(g) + 
  geom_abline(aes(intercept = 1, slope =  1), color = "red")

>>>>

catchshare_pred_plot <- orig_itq_broad_fit %>%
  ggplot(aes(pred, CatchShare == 1, fill = CatchShare == 1)) +
  ggridges::geom_density_ridges(show.legend = FALSE, alpha = 0.75) +
  geom_vline(aes(xintercept = 0.5), linetype = 2, color = "red") +
  labs(y = "Is Catch Share?",
       x = "Probability of Catch Share",
       caption = "Classified as catch share if p>0.5") +
  scale_x_continuous(limits = c(0, 1), expand = c(0, .01))

@@

pROC::ggroc(g) + 
  geom_abline(aes(intercept = 1, slope =  1), color = "red") + 
  labs(x = "")
